Flatiron data cleaning report and questions

### 2021-03-17 Rmd/Report cleaning.Rmd
New Rmd Flatiron analysis

---
title: "Flatiron data cleaning and analysis report"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: flatly
    highlight: pygments
    df_print: paged
---

>>>>

---
title: "Flatiron data cleaning report and questions"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: flatly
    highlight: pygments
    df_print: paged
---
